### 2019-09-23 uiuc.tex
updated about UIUC, in progress

\section{Urbana-Champaign and UIUC}

\subsection{About Urbana-Champaign}
Champaign-Urbana (CU) is a close-knit community filled with music, culture, and food. While Campustown, the neighborhood immediately surrounding campus,  is an important part of the atmosphere, there is plenty to do off campus. Relax in one of the outdoor restaurants downtown or walking through the various gardens and parks around town. The culture in Champaign is very rich as a result of many annual festivals such as the CU Pride Parade, the Ellnora guitar festival, and the Pygmalion festival. The Krannert Center for the Performing Arts is also a world-renowned theater that has hosted groups from all genres like the New York Philharmonic, the Russian National Ballet, and Sonny Rollins.

@@

@@

\subsection{About the University of Illinois}
Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions. The theory of superconductivity, the invention of the transistor, the discovery of archaea, the fourth domain of life, and the first web browser are just some of the many breakthroughs from UIUC. Established in 1876, the famous Morrow Plots became the first research crop field at a university and is still used today. Attendees will also be familiar with Blue Waters, one of the world’s fastest supercomputers. 
The UIUC Grainger College of Engineering has had sixteen Nobel Laureates in physics. Including John Bardeen, the only scientist to ever win the award twice. It also offers 15 different majors to more than 9,100 undergraduate and 3,400 graduate students. Of its twelve ranked majors, nine are ranked among the top 10 in the nation, and six of which remain ranked among the top 5 in their degree. Overall, the College of Engineering in Urbana-Champaign ranks sixth among the nation’s best undergraduate engineering programs. With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its 45,000 students the ability to succeed.\\
Today, the University of Illinois at Urbana-Champaign attracts visitors from throughout the state by offering a variety of valuable public attractions. UIUC maintains four public museums: the Spurlock Museum, containing 54,000 cultural artifacts from around the world; the Illinois Natural History Survey, has more than 9.5 million biologic specimens in its collection; the Sousa Archives and Center for American Music, provides shows and education to students and the public; and the Krannert Art Museum, offers fine arts and education. More than 470,000 square feet of recreational space is occupied by other facilities including an ice arena, climbing wall, swimming pools, parks, sports fields, parks, and outdoor adventure venues.

>>>>

\section{East-central Illinois: The cities of Champaign and Urbana}

\subsection{Champaign-Urbana in a Nutshell}
%Champaign-Urbana (CU) is a close-knit community filled with music, culture, and food. While Campustown, the neighborhood immediately surrounding campus,  is an important part of the atmosphere, there is plenty to do off campus. Relax in one of the outdoor restaurants downtown or walking through the various gardens and parks around town. The culture in Champaign is very rich as a result of many annual festivals such as the CU Pride Parade, the Ellnora guitar festival, and the Pygmalion festival. The Krannert Center for the Performing Arts is also a world-renowned theater that has hosted groups from all genres like the New York Philharmonic, the Russian National Ballet, and Sonny Rollins.

Champaign-Urbana (CU), or colloquially known as Chambana, is home to the flagship campus of the University of Illinois system, the University of Illinois at Urbana-Champaign (UIUC). Since its foundations in the mid 19th century, it has flourished into the cultural hub of the midwest that it is today. CU houses many landmarks and districts, and it showcases both community and nationwide events annually. It is home to the Historic Virginia Theater, host to Ebertfest in honor of the late film critic and UIUC alumnus Roger Ebert. The Krannert Center for the Performing Arts is located on U of I campus, which is known for its four first-class venues, including the Foellinger Great Hall - one of the most acoustically perfect performance spaces in the world, attracting world famous artists and ensembles to perform there every year. Other notable events that attract many people to the twin cities are the Pygmalion Music Festival, the Urbana Sweetcorn Festival, and the Illinois Marathon.

CU is an industrial base to several major companies. This encompasses offices for Abbott Laboratories, Archer Daniels Midland (ADM), Caterpillar, John Deere, The Dow Chemical Company (TDCC), IBM, and State Farm. Other top employers in CU include Kraft Heinz, Carle Foundation Hospital, Jimmy John's, and high technology employer Wolfram Research. Carle has notably been affiliated with the creation of the first college in CU in over 60 years, the Carle Illinois College of Medicine -  ``the world's first engineering-based college of medicine". Research Park at the University of Illinois serves as a technology hub for several research and development ventures, where there are more than 120 companies employing 2,100 students and professionals in high-technology careers. Over 70 startup companies work in commercializing technology in Research Park.

@@

\subsubsection{Accommodations}
Information about facility/hotel space/capacity goes here - reference UNLV 2012, UPenn 2014, UW 2016

@@

\subsection{University of Illinois at Urbana-Champaign: Learning \& Labor}
Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions. The theory of superconductivity, the invention of the transistor, the discovery of archaea, the fourth domain of life, and the first web browser are just some of the many breakthroughs from UIUC. Established in 1876, the famous Morrow Plots became the first research crop field at a university and is still used today. Attendees will also be familiar with Blue Waters, one of the world’s fastest supercomputers. 
The UIUC Grainger College of Engineering has had sixteen Nobel Laureates in physics. Including John Bardeen, the only scientist to ever win the award twice. It also offers 15 different majors to more than 9,100 undergraduate and 3,400 graduate students. Of its twelve ranked majors, nine are ranked among the top 10 in the nation, and six of which remain ranked among the top 5 in their degree. Overall, the College of Engineering in Urbana-Champaign ranks sixth among the nation’s best undergraduate engineering programs. With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its 45,000 students the ability to succeed.\\
Today, the University of Illinois at Urbana-Champaign attracts visitors from throughout the state by offering a variety of valuable public attractions. UIUC maintains four public museums: the Spurlock Museum, containing 54,000 cultural artifacts from around the world; the Illinois Natural History Survey, has more than 9.5 million biologic specimens in its collection; the Sousa Archives and Center for American Music, provides shows and education to students and the public; and the Krannert Art Museum, offers fine arts and education. More than 470,000 square feet of recreational space is occupied by other facilities including an ice arena, climbing wall, swimming pools, parks, sports fields, parks, and outdoor adventure venues.
